Barneby Lives usage example

### 2023-05-18 scripts/project_template.Rmd
function to convert datum to sf objects and convert all 2 wgs84

```{r dummy data}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 1000), seq(1:1000)),
  day = c(sample(1:31, size = 1000, replace = T)),
  month = c(sample(5:10, size = 1000, replace = T)),
  year = 2023,
  longitude = runif(1000, min = -120, max = -100), 
  latitude = runif(1000, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'longitude', y = 'latitude'), crs = 4326, remove = F)

@@

```{r coordinate parsing if required}

 out <- dms2dd(dummy_pts)

 x <- x |>
    dplyr::relocate(any_of(
      c('longitude_dms', 'latitude_dms', 'latitude_dd', 'longitude_dd')), 
    .before = last_col())
```

>>>>

```{r dummy data}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 1000), seq(1:1000)),
  day = c(sample(1:31, size = 1000, replace = T)),
  month = c(sample(5:10, size = 1000, replace = T)),
  year = 2023,
  datum = sample(c('nad83', 'nad27', 'wgs84'), size = 1000, replace = T),
  longitude = runif(1000, min = -120, max = -100), 
  latitude = runif(1000, min = 35, max = 48)
)

@@

```{r coordinate parsing and make object spatial in wgs84}

out <- dms2dd(dummy_pts)
d <- coords2sf(out)
